Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-26 WSSSPE1_report/WSSSPE1_summary_report.tex
restructure sentence

Because progress in scientific research is dependent on the quality and
accessibility of software at all levels, it is now critical to address many
challenges related to the development, deployment, and maintenance of reusable
software.
%\note{Ketan: What are the levels in scientific process where software
%is required. It might be interesting to outline these stages and types of
%software required in each stage.}
In addition, it is essential that scientists,
researchers, and students are able to learn and adopt software-related skills
and methodologies. Established researchers are already acquiring some of these
skills, and in particular a specialized class of software developers is
emerging in academic environments who are an integral and embedded part of
successful research teams. The WSSSPE workshop was intended to provide a forum
for discussion of the challenges, including both positions and experiences. The
short papers and debates have been archived to provide a basis for continued
discussion, and the workshop has fed into the collaborative writing of this
journal publication. An estimate of 90 to 150 participants were present 
throughout the day. Additional papers based on extended versions of workshop
submissions are expected.  The level of interest in the workshop has led the
organizers, working with some of the submitters and attendees, to plan two
additional workshops (at the 2014 SciPy and SC14 conferences) and to turn the
workshop website into a community website that can be used as a focus for
further discussion and progress.  Additionally, a minisymposium at 2014 SIAM
Annual Meeting on ``Reliable Computational
Science'' that aims to further explore some of the key issues raised in WSSSPE
is co-organized by a WSSSPE1 participant.

>>>>

Because progress in scientific research is dependent on the quality and
accessibility of software at all levels, it is now critical to address many
challenges related to the development, deployment, and maintenance of reusable
software.
%\note{Ketan: What are the levels in scientific process where software
%is required. It might be interesting to outline these stages and types of
%software required in each stage.}
In addition, it is essential that scientists,
researchers, and students are able to learn and adopt software-related skills
and methodologies. Established researchers are already acquiring some of these
skills, and in particular a specialized class of software developers is
emerging in academic environments who are an integral and embedded part of
successful research teams. The WSSSPE workshop was intended to provide a forum
for discussion of the challenges, including both positions and experiences. The
short papers and debates have been archived to provide a basis for continued
discussion, and the workshop has fed into the collaborative writing of this
journal publication. An estimate of 90 to 150 participants were present 
throughout the day. Additional papers based on extended versions of workshop
submissions are expected. The level of interest in the workshop has led the
organizers, working with some of the submitters and attendees, to plan two
additional workshops (at the 2014 SciPy and SC14 conferences) and to turn the
workshop website into a community website that can be used as a focus for
further discussion and progress. Additionally, a minisymposium that aims to
further explore some of the key issues raised in WSSSPE is co-organized by a
WSSSPE1 participant at the 2014 SIAM Annual Meeting on ``Reliable
Computational Science''.
